Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-04-26 paper-correlations.tex
Calculate CFs for 3D data

For demonstration purposes, we computed correlation functions for images of
sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
dimensions $1000 \times 1000$. The result can be seen on \cref{fig:real-data}.

>>>>

For demonstration purposes, we computed correlation functions for images of
sandstone found on Digital Rocks Portal \cite{DigitalRocks} all of which have
dimensions $1000 \times 1000 \times 1000$. The result can be seen on
\cref{fig:real-data}.
